Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-06-26 nge.tex
Formatting
minor reduction.

NGE exposes an API to describe workloads (Fig.~\ref{fig:arch-overview}, green
squares) and pilots (Fig.~\ref{fig:arch-overview}, red circles), and to
instantiate a PilotManager and a UnitManager.   The PilotManager submits
pilots to Titan's PBS  batch system via SAGA API (Fig.~\ref{fig:arch-overview}, dash arrow), as done by PanDA Broker to submit MPI scripts. Once
scheduled, the pilot's Agent is bootstrapped on Titan's MOM node and
the Agent's Executors on the on the worker
nodes, and the UnitManager schedules units to the Agent's Scheduler
(Fig.~\ref{fig:arch-overview}, solid arrow). The Agent's Scheduler schedules
the units on one or more Agent's Executor for execution. The Agent's executors
can manage one or more worker nodes, depending on performance evaluations. The
UnitManager and the Agent communicate via a database that is instantiated on
one of Titan's DTN so as to be reachable by both modules.

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for
communication and coordination of the execution of units. This environment is
a critical component of the OpenMPI implementation, developed to support
distributed high-performance computing applications operating in a
heterogeneous environment~\cite{castain05:_open_rte, cug-2016}. ORTE provides
a mechanism to create a \emph{``dynamic virtual machine''} (DVM) that spans
multiple nodes. The DVM transparently provides support for interprocess
communication, resource discovery and allocation, and process launching across
a variety of platforms. Libraries enable the interaction between users and
ORTE to enable the submission, monitoring and managing of tasks, avoiding
filesystem bottlenecks and race conditions with network sockets. As a
consequence, ORTE is able to minimize the system overhead while submitting
tasks.

>>>>

NGE exposes an API to describe workloads (Fig.~\ref{fig:arch-overview}, green
squares) and pilots (Fig.~\ref{fig:arch-overview}, red circles), and to
instantiate a PilotManager and a UnitManager.   The PilotManager submits
pilots to Titan's PBS  batch system via SAGA API (Fig.~\ref{fig:arch-
overview}, dash arrow), as done by PanDA Broker to submit MPI scripts. Once
scheduled, the pilot's Agent is bootstrapped on Titan's MOM node and the
Agent's Executors on the on the worker nodes, and the UnitManager schedules
units to the Agent's Scheduler (Fig.~\ref{fig:arch-overview}, solid arrow).
The Agent's Scheduler schedules the units on one or more Agent's Executor for
execution. The Agent's executors can manage one or more worker nodes,
depending on performance evaluations. The UnitManager and the Agent
communicate via a database that is instantiated on one of Titan's DTN so as to
be reachable by both modules.

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for
communication and coordination of the execution of units. This environment is
a critical component of the OpenMPI implementation ~\cite{castain05:_open_rte,
cug-2016}. ORTE is able to minimize the system overhead while submitting tasks
by avoiding filesystem bottlenecks and race conditions with network sockets.

% The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for
% communication and coordination of the execution of units. This environment is
% a critical component of the OpenMPI implementation, developed to support
% distributed high-performance computing applications operating in a
% heterogeneous environment~\cite{castain05:_open_rte, cug-2016}. ORTE provides
% a mechanism to create a \emph{``dynamic virtual machine''} (DVM) that spans
% multiple nodes. The DVM transparently provides support for interprocess
% communication, resource discovery and allocation, and process launching across
% a variety of platforms. Libraries enable the interaction between users and
% ORTE to enable the submission, monitoring and managing of tasks, avoiding
% filesystem bottlenecks and race conditions with network sockets. As a
% consequence, ORTE is able to minimize the system overhead while submitting
% tasks.
